AIR4Children: Artificial Intelligence and Robotics for Children

### 2021-03-03 article/tex/main.tex
polishes introduction with D_Cruz contributions

%\usepackage[%
%    style=ieee,
%    dashed=false,
%    doi=false,
%    isbn=false,
%    giveninits=true,
%    maxnames=10,
%]{biblatex}
%\usepackage{biblatex}
%\addbibresource{../references/references-simple.bib}

@@

\author{air4children}
\affiliation{%
  %\institution{University of A}
  %\streetaddress{Adress}
  \city{Xicohtzinco}
  \country{M\'exico}}
%\authornotemark[1]
\email{air4children@gmail.com}

@@

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{air4children}

@@

\section{Introduction} 
The scientific and technological progress in the fields of Artificial Intelligence and Robotics (AIR) has been rapidly moving forward over the past decade with special focus in countries such as United States, China and Europe where support of such fields is part of their agenda \cite{Savage2020}. 
However, such progress also brings other challenges such as the little to none focus on a centred AIR for children as well as the challenge of making the fields of AIR available to under-represented communities.
With regard to child-centered AIR, there is few materials and resources with poor accessible and not appropriately affordable.  
In terms of affordability, such technologies are unreachable to young audiences from under-represented communities as recently pointed out by United Nations Children's Fund (UNICEF) \cite{UNICEF2020}.
Therefore, this work is proposing Artificial Intelligence and Robotics for Children (AIR4Children) as a way to make AIR available to young audiences with perhaps limited resources and to creation and design tools based on open-sourced projects to address fairness and accessibility. 
Additionally, AIR4Children is aiming to design curriculums with an non-traditional education approach for children of different socio economical backgrounds, developmental stages or learning abilities.

For this work, as a way to minimise cost for hardware and software, section 2 review open source project as the basis of the material for AIR4Children.
In section 3, it is presented three stages of AIR4Children including open source materials and teaching materials based on Montessori education. 
We then conclude this work with current status of AIR for children, open source materials for hardware, software and teaching and add few words on the future work as a way to mitigate few of the challenges cited above.

@@

\subsection{Open teaching materials}
Considering teaching materials of AI and Robotics to be child-like oriented, AIR4Children is then adopting Montessori's education with philosophy orbited around the quote “the hand is the instrument of the mind.” \cite{montessori2013absorbent}.
In that way, materials for AIR4Children are based on Montessori education with the aim to help children to internalise new concepts and to develop concentration of their learning skills through activities of movement and repetition.
%For instance, the best way a child can concentrate is by fixing his attention on some task he is performing with his hands. 
One potential way to develop such skills is by designing activities in AI and robotics that are appropriately introduced in development stages \cite{bers2008, bers-horn2010, kazakoff-bers2012} as well as the development of grasping and understanding mathematical concepts (e.g. numbers, size, and shapes) and computational thinking (e.g. variables, loops, counters, etc) \cite{bers2012, resnick1998}.
Similarly, as Elkin et al. (2014) \cite{elkin2014} explained, air4children can provide a way to engage children in problem-solving activities based on Montessori education as well as design activities that allow children to participate in creative explorations, develop fine motor skills, hand-eye coordination, engage in collaborative and teamwork activities.

@@

As a future work, air4children aims to run workshops by the end of 2021 to put in practice educational material of child-centre AI and robotics and to evaluate the impact on these fields to children and to the community.

@@

%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
To Rocio Montenegro for her input as Montessori teacher. To Elva Corona for her contributions on giving vision to the goals of the project. 
To Marta Perez, Donato Badillo Jr and Antonio Badillo for their interest and initial testers of the project. 
To Angel Mandujano for his help on the preparation of the software frameworks for the project. 
To all of you of whom has limited time and had not able you to contributed as you wished in the project.
Thanks everyone to believe in this project, good things are ahead of us. Miguel Xochicale.
\end{acks}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{../references/references-simple}
%\printbibliography

>>>>

@@

\author{AIR4Children}
\affiliation{%
  %\institution{University of A}
  %\streetaddress{Adress}
  \city{Xicohtzinco}
  \country{M\'exico}}
%\authornotemark[1]
\email{air4children@gmail.com}

@@

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{AIR4Children}

@@

\section{Introduction} 
The scientific and technological progress in the fields of Artificial Intelligence and Robotics (AIR) has been rapidly moving forward over the past decade with special focus in countries such as United States, China and Europe where support of such fields is part of their agenda \cite{Savage2020}. 
Artificial Intelligence (AI), for instance, is changing and helping various aspects of our daily lives, from entertainment to complex medicine discovery tasks. 
Then the democratization of current AI technologies allows people without in-depth skills in maths, statistics, and programming to create their own AI solutions. Examples of these new open-source platforms with a high-level programming approach are PyTorch, TensorFlow, Keras, and Scikit-learn. 
However, most of these technologies use specific syntax and grammar and work with particular programming languages which makes the learning curve a complex task for children. 
Therefore, there is research to be done in order to design and create open-source platforms that bring children closer to AI.
Something similar happen in the case of Robotics where software-based AI solutions can deploy solutions on real robots (such as JIBO, NAO, others), however these robots are generally inaccessible for children worldwide, particularly for those of under-represented communities.
Such challenges of unreachable technologies in AI, and extrapolated to Robotics, to young audiences 
also include their affordability and open accessibility \cite{UNICEF2020}.

Therefore, this work coins the term of Artificial Intelligence and Robotics for Children (AIR4Children) as a way to make AI and Robotics available to young audiences from under-represented communities as well as to create and to design tools based on open-sourced projects.
Additionally, AIR4Children aims to create, to design and to distill curriculums based on non-traditional education (i.e. Montessori) for children of different socio-economical background, developmental stages and learning abilities.

For this work, section 2 reviews open source projects as the basis of the material for AIR4Children.
Section 3 introduces AIR4Children as a open source project with open teaching materials based on Montessori education. 
We then conclude with current status of AIR for children, the creation of open source materials for hardware, software and teaching resources and mentions the future work for pilots and distillation of teaching materials.

@@

\subsection{Open teaching materials}
Considering teaching materials of AI and Robotics to be child-like oriented, AIR4Children is then adopting Montessori's education with philosophy orbited around the quote “the hand is the instrument of the mind.” \cite{montessori2013absorbent}.
In that way, materials for AIR4Children are based on Montessori education with the aim to help children to internalise new concepts and to develop concentration of their learning skills through activities of movement and repetition.
%For instance, the best way a child can concentrate is by fixing his attention on some task he is performing with his hands. 
One potential way to develop such skills is by designing activities in AI and robotics that are appropriately introduced in development stages \cite{bers2008, bers-horn2010, kazakoff-bers2012} as well as the development of grasping and understanding mathematical concepts (e.g. numbers, size, and shapes) and computational thinking (e.g. variables, loops, counters, etc) \cite{bers2012, resnick1998}.
Similarly, as Elkin et al. (2014) \cite{elkin2014} explained, AIR4Children can provide a way to engage children in problem-solving activities based on Montessori education as well as design activities that allow children to participate in creative explorations, develop fine motor skills, hand-eye coordination, engage in collaborative and teamwork activities.

@@

As a future work, AIR4Children aims to run workshops by the end of 2021 to put in practice educational material of child-centre AI and robotics and to evaluate the impact on these fields to children and to the community.

@@

%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
To Rocio Montenegro for her contributions and input as Montessori teacher. 
To Elva Corona for her contributions on giving vision to the goals of the project. 
To Marta P\'erez, Donato Badillo-Per\'ez and Antonio Badillo-Per\'e\ for their interest as initial testers of the project. 
To Leticia Vazques for her inputs as a teacher of teenagers. 
To Angel Mandujano for his help on the preparation of the software frameworks for the project. 
To Dago Cruz for his contributions on open source AI and Robotics.
To all of you of whom with the limited time were able to contribute to this work to make it more solid.
Thanks to Miguel Xochicale to orchestrate this project.
\end{acks}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{../references/references}
